\documentclass[a4paper,11pt]{article}  
\usepackage{latexsym} 
\usepackage[empty]{fullpage} 
\usepackage{titlesec} 
\usepackage{marvosym} 
\usepackage{enumitem} 
\usepackage[hidelinks]{hyperref} 
\usepackage{xcolor} 
\usepackage{fontawesome}  

% Adjust margins 
\addtolength{\oddsidemargin}{-0.375in} 
\addtolength{\evensidemargin}{-0.375in} 
\addtolength{\textwidth}{0.75in} 
\addtolength{\topmargin}{-0.5in} 
\addtolength{\textheight}{1.0in}  

\urlstyle{same} 
\raggedbottom 
\raggedright  

% Compact itemize spacing
\setlist{nosep}  

% Sections formatting (bold + line under) 
\titleformat{\section}{\vspace{-4pt}\bfseries\raggedright\large }{}{0em}{}[\titlerule\vspace{-5pt}]  

%-------------------------------------------
% Resume starts here 
\begin{document}  

%-----------Header----------------- 
\begin{center}     
    {\Huge \scshape Krishna Dhake} \\[4pt] 

    % First row: phone, email, linkedin
    \faPhone \, 876-762-8679 \quad
    \faEnvelope \, \href{mailto:kgdhake2005@gmail.com}{kgdhake2005@gmail.com} \quad
    \faLinkedin \, \href{https://linkedin.com/in/krishna-dhake}{linkedin.com/in/krishna-dhake} 
    \\[4pt]

    % Second row: github only
    \faGithub \, \href{https://github.com/kgdhake}{github.com/kgdhake} 
\end{center}     

%-----------Education----------------- 
\section{Education} 

\textbf{Veermata Jijabai Technological Institute}, Mumbai \hfill Jul 2023 -- Present \\ 
Bachelor of Technology in Electronics and Telecommunication \& Minor in CyberSecurity \\[4pt]  

\textbf{Bhusawal Arts, Science and PO Nahata College of Commerce}, Bhusawal \hfill Jul 2021 -- May 2023 \\ 
HSC: 79.83\% \quad | \quad JEE Mains: 95.46\%ile \quad | \quad MHTCET: 99.36\%ile \\[4pt]  

\textbf{Tapti Public School}, Bhusawal \hfill Sep 2010 -- May 2021 \\ 
SSC: 79.83\%    

%-----------Projects----------------- 
%-----------Projects----------------- 
\section{Projects} 

\faGithub \, \href{https://github.com/kgdhake/Video-Streaming-App}{\textbf{Streamify}} 
\, | JavaScript, MongoDB, React, Express, Node.js \hfill May 2025 
\begin{itemize}[leftmargin=*]   
    \item Developed a full-stack real-time language exchange platform with authentication, friend requests, and live chat/video via Stream API.   
    \item Implemented secure authentication using JWT and protected API routes.   
    \item Designed responsive UI with React, Tailwind CSS, and DaisyUI including notifications and dashboards. 
\end{itemize}  

\faGithub \, \href{https://github.com/kgdhake/weather-/tree/master}{\textbf{Weather App}} 
\, | React, Express, Cesium, Node \hfill Jun 2025 
\begin{itemize}[leftmargin=*]   
    \item Built a 3D globe-based weather application with OpenWeatherMap API integration.   
    \item Used React with Vite frontend and Express backend for secure API requests.   
    \item Implemented popup components with real-time weather info and error handling. 
\end{itemize} 


%-----------Relevant Coursework----------------- 
\section{Relevant Coursework} 
\begin{itemize}[leftmargin=*]   
    \item Data Structures   
    \item Database Management   
    \item Web Development   
    \item Linear Integrated Circuits   
    \item Signal and System 
\end{itemize} 

%-----------Technical Skills----------------- 
\section{Technical Skills} 
\textbf{Languages:} Java, HTML/CSS, JavaScript, SQL \\ 
\textbf{Developer Tools:} VS Code, IntelliJ, Git/GitHub \\ 
\textbf{Technologies/Frameworks:} Linux, Express.js, React.js, Next.js, Material UI, Tailwind CSS  

%-----------Achievements----------------- 
\section{Achievements} 
\begin{itemize}[leftmargin=*]   
    \item Solved 360+ LeetCode Problems   
    \item 1032 rating on CodeChef 
\end{itemize} 

%-----------Leadership / Extracurricular----------------- 
%-----------Leadership / Extracurricular----------------- 
\section{Leadership / Extracurricular} 

\textbf{EESA} --- \textit{Head Of Operation} \hfill Aug 2025 -- Present
\begin{itemize}[leftmargin=*] 
    \item Coordinated and managed the logistics of technical workshops, guest lectures, and hands-on sessions, ensuring smooth execution of events related to electronics and electrical engineering.
    \item Supervised committee members, delegated tasks effectively, and managed resources (venue, equipment, schedules) to maintain efficiency and professionalism in all association activities.
\end{itemize} 

\textbf{Technovanza} --- \textit{Operations} \hfill Aug 2024 - July-2025
\begin{itemize}[leftmargin=*] 
    \item Coordinated and managed operations for Technovanza, the college-wide technical festival involving multi-disciplinary workshops, events, and guest lectures.
\end{itemize}

\end{document}
